\documentclass{article}

\usepackage{libertine}
\usepackage{microtype}

\title{Museum Lighting, Colour Constancy and Melanopsin.}
\date{} 

\begin{document}
\maketitle

\section{Extended Abstract}

Light causes damage to objects in museums. Museums seek a pragmatic compromise between lighting which causes minimal damage to objects, and lighting which allows maximal visitor enjoyment. Generally this is achieved by following industry recommendations for maximum illuminance.

A complementary way to reduce damage, highlighted by the Commission Internationale de l'Eclairage in a 2004 publication, is to choose illumination of a lower Correlated Colour Temperature (CCT), because such illumination will contain most radiation energy in the longer wavelengths, which are generally less damaging to objects. Computations performed for a range of commercially available lighting products showed a strong correlation between predicted damage and CCT, with a factor of two between the low and high CCT sources. Practically, a sensitive object might be displayed for twice as long under a low CCT illuminant than a high one, before passing a damage threshold. 

A series of interviews with museum professionals showed that this technique is not currently being employed. One reason is a belief that changing the CCT in an environment will affect the visual experience and the atmosphere in the room.

Models of vision suggest that a change in CCT alone should not affect visual experience; that in a space with a single type of lighting we should be able to adapt to any colour of illumination. This seems at most only partially true. It is true that we seem to adapt to the ambient illuminant, both in terms of luminance and chromaticity, such that our perception of object colours relates primarily to object reflectance properties rather than the absolute intensities reaching our eyes. Generally, however, we do also seem to have an awareness of the properties of the illumination in a scene, and even a preference for some illuminants over others. Historically, experiments seeking to find an ideal preferred CCT have provided conflicting results.

One possible reason for these conflicting results might be if a cell group called the `intrinsically photosensitive Retinal Ganglion Cells' (ipRGCs) were involved in colour constancy. This cell group has traditionally been considered as having no output to visual pathways, and so colour constancy experiments haven't controlled for ipRGC activation, but recent research has shown that ipRGCs do in fact have a limited input to visual pathways. There are a range of reasons that suggest that they may play a role in colour constancy specifically.

To investigate the effect of different levels of ipRGC activation on an observer's state of colour constancy,	two lab-based psychophysical experiments were performed. The first sought to examine the effect of different wavelengths of light upon chromatic adaptation. Within a Ganzeld viewing environment, illuminated by one of 16 different wavelengths of near-monochromatic light, observers performed an achromatic setting task, controlling the chromaticity of a display visible in the central field through a 4° circular aperture with two handheld sliders.

In the second experiment the role of melanopsin in chromatic adaptation was more directly questioned. The same task was performed as in the first experiment, but the Ganzfeld was this time illuminated by one of two perceptually metameric lights with different melanopic irradiance levels. Neither of these experiments provided evidence for a simple or strong effect of ipRGC activation, though this is limited to the case where peripheral stimulation would affect central perception.

Concurrently, a method for performing colour constancy experiments outside of the lab environment, which could be completed quickly and with naive observers, was developed. 

Following these experiments a different approach was adopted: rather than asking what the affect of varying ipRGC activation upon experimental subjects was, instead the question was posed whether an ipRGC-based signal could hypothetically be useful for colour constancy, considering what we know of daylight variability and natural surface reflectance properties. A computational methodology was employed. It was found that the spectral sensitivity of melanopsin is optimal for providing a signal which can transform raw chromatic signals to an illuminant-independent space, and that this can be done without using any scene level assumptions such as grey-world.

The applied goal of this research was to increase our understanding of colour constancy so as to advise museums on how to reduce damage to objects without degrading visitor experience. Asking whether ipRGCs play a role in colour constancy is additionally valuable to the vision science community, and to lighting engineering applications beyond the museum world.


\end{document}